% -----------------------------------------------------------------------------
% Created:      2022-01-27
% Description:  Write-up of JH notebook and file log
%
% Requires:     csvsimple 
% -----------------------------------------------------------------------------

\documentclass[a4paper]{article}


% csvsimple package is required to load text from CSV files into tabular form
\usepackage{csvsimple}
\usepackage{xstring}
\usepackage{longtable}
\usepackage[table]{xcolor}
\usepackage{hyperref}

% array package for column modifications (emphasis)
\usepackage{array}

% for convering datetimes
\usepackage[british,showdow]{datetime2}

\usepackage{tikz}

\newcommand\hfaprestable[9]{
    % Arguments
    %   1 - filename
    %   2 - number of sub bursts
    %   3 - number of attenuator settings
    %   4 - AF gain (list)
    %   5 - RF attenuator (list)
    %   6 - lower frequency
    %   7 - upper frequency
    %   8 - chirp period
    %   9 - location
    %  10 - comments
    \def\temphftfolder{#1}
    \def\temphftfilename{#2}%
    \def\temphftsubbursts{#3}%
    \def\temphftnoattn{#4}
    \def\temphftaf{#5}%
    \def\temphftrf{#6}%
    \def\temphftlowfreq{#7}%
    \def\temphftupfreq{#8}%
    \def\temphftchirp{#9}%
    \hfaprestablecont
}

\newcommand{\afrftable}[1]{& #1}
\newcommand{\hfaprestablemcol}[1]{%
    % \multicolumn{4}{p{9cm}}{#1}%
    {#1}
}
\newcommand{\hfaprestablecont}[3]{
    \def\temphftlocation{#1}%
    \def\temphftcomment{#2}%
    \begin{table}[h]
        \centering
        \renewcommand{\arraystretch}{1.5}%
        \begin{tabular}{>{\columncolor{gray!10}}l p{9cm}}%
            \hline%
            \textbf{Folder} & \hfaprestablemcol{\ttfamily\url{\temphftfolder}} \\ % filename
            \textbf{Filename} & \hfaprestablemcol{\ttfamily\temphftfilename} \\ % filename
            \hline%
            Subbursts & \hfaprestablemcol{\temphftsubbursts} \\ %
            Attenuator Settings & \hfaprestablemcol{\temphftnoattn} \\ %
            AF Gain (dB) & 
            % \begin{tabular}{l l l l}
                \StrSubstitute{\temphftaf}{,}{, } \\%
            % \end{tabular}
            RF Attenuation (dB) & \StrSubstitute{\temphftrf}{,}{, } \\%
            \hline %
            Bandwidth ($B$) & \hfaprestablemcol{\temphftlowfreq~MHz to \temphftupfreq~MHz} \\ %
            Chirp Period ($T$) & \hfaprestablemcol{\temphftchirp~s} \\ %
            \hline %
            Location & \hfaprestablemcol{\temphftlocation} \\ %
            \hline %
            Comments & \hfaprestablemcol{\temphftcomment} \\ %
            \hline %
        \end{tabular} %
        \caption{File summary for \texttt{\temphftfilename}.}
        \label{tab:#3}
    \end{table}
    \clearpage
}

% -----------------------------------------------------------------------------
% Define command for database defintion tables
\newcommand{\sqlspectable}[2]{
    \renewcommand{\arraystretch}{1.5}
    \rowcolors{2}{gray!10}{white}
    \begin{longtable}{l l >{\raggedright}p{3cm} >{\raggedright\arraybackslash}p{4cm}}
        \caption{#2} \\
        \hline
        \textbf{Fieldname} & \textbf{Datatype} & \textbf{Parameters} & \textbf{Description}\\
        \hline
        \endhead
        \hline
        \endfoot
        #1
    \end{longtable}
}

% -----------------------------------------------------------------------------
% Define new date style for subsection titles

% -----------------------------------------------------------------------------
% Title
\title{\textbf{Notebook Summary for HF ApRES Experiments}}
\author{J.D.~Hawkins}

\begin{document}

    \maketitle
    
    \newpage

    \tableofcontents

    \newpage

    \section{Database Structure}

    \subsection{Table `\texttt{measurements}'}
    \sqlspectable{
        %
        measurement\_id & INTEGER & PRIMARY KEY & 
        Unique identifier for each file. \\
        %
        filename & TEXT & NOT NULL & 
        Filename without path. \\
        %
        path & TEXT & UNIQUE NOT NULL&
        Path to file in UNIX form, relative to top-level project root. \\
        %
        name & TEXT & - &
        The name associated with the measurement, used to group sets of 
        measurements together. \\
        %
        timestamp & TEXT & UNIQUE ASC NOT NULL &
        \texttt{YYYY-mm-dd HH:MM:SS.fff} formatted timestamp according to
        time and date the measurement was taken. \\
        %
        valid & INTEGER & NOT NULL DEFAULT 0 &
        Boolean indicator of whether file is valid. Assumes invalid by 
        default. \\
        %
        location & TEXT & - & 
        Measurement location name. \\
        % 
        comments & TEXT & - &
        Description and comments for measurement if relevant. \\
        % 
        latitude & REAL & - &
        Latitude of measurement location if known. \\
        %
        longitude & REAL & - & 
        Longitude of measurement location if known. \\
        %
        elevation & REAL & - & 
        Elevation of measurement location if known (referenced to WGS84). \\
    }
    {Specification for \texttt{measurements} table.}
    
    \newpage

    \subsection{Table `\texttt{apres\_metadata}'}
    The fields \texttt{id} and \texttt{burst\_id} make a unique pair to ensure
    that each burst within a \texttt{*.dat} file is only represented once.

    \sqlspectable{
        %
        id & INTEGER & PRIMARY KEY & 
        Unique identifier for metadata.  Distinct from \texttt{measurement\_id}
        in that each \texttt{*.dat} file can have multiple bursts.\\
        %
        burst\_id & INTEGER & NOT NULL &
        Identifies the burst within a \texttt{*.dat} the metadata represents.\\
        %
        measurement\_id & INTEGER & NOT NULL & 
        Identifies the file record where the metadata originates from. \\
        %
        % header\_index & INTEGER & NOT NULL DEFAULT 0 &
        % Indicates the byte at which to start reading the header \\
        % % 
        % burst\_index & INTEGER & NOT NULL & 
        % Indicates the byte at which to start reading the data associated with the burst \\
        %
        \hline
        \multicolumn{4}{c}{\textit{ApRES Specific Metadata}} \\
        \hline
        %
        timestamp & TEXT & NOT NULL & 
        \texttt{YYYY-mm-dd HH:MM:SS.fff} formatted timestamp as logged in
        \texttt{*.dat} file. \\
        %
        n\_attenuators & INTEGER & NOT NULL CHECK(\textgreater 0, \textless 5) & 
        Number of attenuator settings used. \\
        %
        n\_chirps & INTEGER & NOT NULL CHECK(\textgreater 0) & 
        Total number of individual chirps in file. \\
        %
        n\_subbursts & INTEGER & NOT NULL CHECK(\textgreater 0) &
        Number of sub-bursts (repeats) of the burst configuration. \\
        %
        period & REAL & NOT NULL CHECK(\textgreater 0) & 
        Chirp period in seconds. \\
        %
        f\_lower & REAL & NOT NULL CHECK($\ge$ 0) &
        Lower bound of chirp ramp in Hertz. \\
        %
        f\_upper & REAL & NOT NULL CHECK($\ge$ 0) & 
        Upper bound of chirp ramp in Hertz. \\
        %
        af\_gain & TEXT & NOT NULL &
        Comma separated values indicating AF gain settings. \\
        %
        rf\_attenuator & TEXT & NOT NULL & 
        Comma separated values indicating RF attenuator settings. \\
        %
        f\_sampling & REAL & NOT NULL CHECK(\textgreater 0) & 
        Sampling frequency. \\
        % 
        tx\_antenna & TEXT & NOT NULL &
        Transmit antenna selection in comma separated value format. \\
        % 
        rx\_antenna & TEXT & NOT NULL &
        Receive antenna selection in comma separated value format. \\
        % 
        power\_code & INTEGER & - &
        DDS output current power code, if available (dependent on firmware).\\
        %
        battery\_voltage & REAL & - &
        Battery voltage, if available. \\
        %
        temperature\_1 & REAL & - &
        Measured board temperature from sensor 1. \\
        %
        temperature\_2 & REAL & - & 
        Measured board temperature from sensor 2. \\
        %
        rmb\_issue & TEXT & - & 
        RMB issue number if available. \\
        % 
        vab\_issue & TEXT & - & 
        VAB issue number if available. \\
        %
        venom\_issue & TEXT & - &
        Venom issue number if available. \\
        %
        software\_issue & TEXT & - & 
        VAB firmware issue number if available. \\
    }{
        Specification for \texttt{apres\_metadata} table.
    }
    
    \newpage

    \subsection{Table `\texttt{data}'}
    \sqlspectable{
        data\_id & INTEGER & PRIMARY KEY & 
        Unique identifier for each data item stored in \texttt{/Proc}. \\
        %
        measurement\_id & INTEGER & NOT NULL &
        Linked identified to \texttt{measurements} table for source of
        data. \\
        % 
        filename & TEXT & NOT NULL &
        Filename for processed data item stored in \texttt{/Proc}. \\
        %
        path & TEXT & NOT NULL & 
        Path to file in UNIX form, relative to top-level project root. \\
        %
        timestamp&  TEXT & ASC NOT NULL &
        \texttt{YYYY-mm-dd HH:MM:SS.SSS} formatted timestamp corresponding
        to time at which data was processed. \\
        %
        processing\_steps & TEXT & - & 
        Description of processing steps used to produced data file. \\
        %
    }
    {Specification for \texttt{data} table.}
    

    \newpage

    \section{Testing}
    \DTMsavedate{cdate}{2021-12-27}
    \subsection{\DTMusedate{cdate}}
    \paragraph{20:43:06} \texttt{2021-12-27\_214306.dat} Measurement taken south west of storaage container at Neumayer III
    
    \DTMsavedate{cdate}{2021-12-28}
    \subsection{\DTMusedate{cdate}}

    \DTMsavedate{cdate}{2021-12-29}
    \subsection{\DTMusedate{cdate}}
    % \input{Files/Testing.tex}

\end{document}